Dynein project log

### 2017-02-19 thesis/latex/thesis.tex
Thesis: clean up.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.90\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
  \newcommand\bothbound{\textcolor{blue}{BOTHBOUND}}
  \newcommand\onebound{\textcolor{red}{ONEBOUND}}
  \newcommand\transition{\textcolor{green}{transition?}}
  \begin{tabular}{rll}
    \bothbound &
    1 & \begin{minipage}{5in}
      Bound to microtubule and waiting for ATP to arrive.  The
      conformation is ``post-powerstroke''.
    \end{minipage}\vspace{0.5em}\\
    \bothbound &
    2 & \begin{minipage}{5in}
      ATP has bound to the motor at AAA1, but nothing else has changed.
    \end{minipage}\vspace{0.5em}\\
    \transition &
    3 & \begin{minipage}{5in}
      ``The ring has closed'' in the motor, whatever that means.
    \end{minipage}\vspace{0.5em}\\
    \bothbound &
    4 & \begin{minipage}{5in}
      The affinity to the microtubule is dropped, so it is likely to pop off soon.
    \end{minipage}\vspace{0.5em}\\
    \onebound &
    5 & \begin{minipage}{5in} It has popped off of the microtubule!
      Onebound! The equilibrium angle is also changed.  The ATP has
      been hydrolized, but the phosphate is still bound to the motor.
      ``Priming stroke?''
    \end{minipage}\vspace{0.5em}\\
    \onebound &
    6 & \begin{minipage}{5in} It is now bound to the microtubule, but
      with low affinity, and without any loss of phosphate. Question:
      does this happen many times? If so it may still be onebound.
      Otherwise it is probably bothbound.
    \end{minipage}\vspace{0.5em}\\
    \bothbound &
    7 & \begin{minipage}{5in}
      Now it is seriously bound to the microtubule, and the motor
      domain has changed conformation.  This is now ``high affinity.''
    \end{minipage}\vspace{0.5em}\\
    \bothbound &
    8 & \begin{minipage}{5in}
      Phosphate has been released, and our equilibrium angles have
      been changed.  This is the ``power stroke.''
    \end{minipage}\vspace{0.5em}\\
    \bothbound &
    1 & \begin{minipage}{5in}
      The ADP has been released from the motor domain, so it can now
      bind ATP.  Still ``high affinity,'' and still in the
      ``power-stroke'' conformation.
    \end{minipage}\vspace{0.5em}\\
    \bothbound &
    9 & \begin{minipage}{5in}
      While stuck in this ``normal bound'' state, another site on the
      motor AAA3 can lose its ADP, which leaves the motor in a state
      where it cannot directly move on to step 2 (until after
      reversing this).  Controversial?
    \end{minipage}
  \end{tabular}
  \caption{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
  \label{mech-cycle}
\end{figure}

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[width=.90\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
  \newcommand\bothbound{\textcolor{blue}{BOTHBOUND}}
  \newcommand\onebound{\textcolor{red}{ONEBOUND}}
  \newcommand\transition{\textcolor{green}{transition?}}
  %% \begin{tabular}{rll}
  %%   \bothbound &
  %%   1 & \begin{minipage}{5in}
  %%     Bound to microtubule and waiting for ATP to arrive.  The
  %%     conformation is ``post-powerstroke''.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   2 & \begin{minipage}{5in}
  %%     ATP has bound to the motor at AAA1, but nothing else has changed.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \transition &
  %%   3 & \begin{minipage}{5in}
  %%     ``The ring has closed'' in the motor, whatever that means.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   4 & \begin{minipage}{5in}
  %%     The affinity to the microtubule is dropped, so it is likely to pop off soon.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \onebound &
  %%   5 & \begin{minipage}{5in} It has popped off of the microtubule!
  %%     Onebound! The equilibrium angle is also changed.  The ATP has
  %%     been hydrolized, but the phosphate is still bound to the motor.
  %%     ``Priming stroke?''
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \onebound &
  %%   6 & \begin{minipage}{5in} It is now bound to the microtubule, but
  %%     with low affinity, and without any loss of phosphate. Question:
  %%     does this happen many times? If so it may still be onebound.
  %%     Otherwise it is probably bothbound.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   7 & \begin{minipage}{5in}
  %%     Now it is seriously bound to the microtubule, and the motor
  %%     domain has changed conformation.  This is now ``high affinity.''
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   8 & \begin{minipage}{5in}
  %%     Phosphate has been released, and our equilibrium angles have
  %%     been changed.  This is the ``power stroke.''
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   1 & \begin{minipage}{5in}
  %%     The ADP has been released from the motor domain, so it can now
  %%     bind ATP.  Still ``high affinity,'' and still in the
  %%     ``power-stroke'' conformation.
  %%   \end{minipage}\vspace{0.5em}\\
  %%   \bothbound &
  %%   9 & \begin{minipage}{5in}
  %%     While stuck in this ``normal bound'' state, another site on the
  %%     motor AAA3 can lose its ADP, which leaves the motor in a state
  %%     where it cannot directly move on to step 2 (until after
  %%     reversing this).  Controversial?
  %%   \end{minipage}
  %% \end{tabular}
  \caption{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
  \label{mech-cycle}
\end{figure}

### 2017-02-19 thesis_stuff/thesis_stuff.tex
Thesis: clean up.

\subsection{Single-Molecule Analysis of Dynein processivity and Stepping Behavior}
2006 paper on single-molecule analysis of step sizes of dynein. Might have in-vivo velocity information.

@@

\subsection{Helix sliding in the stalk coiled coil of dynein couples ATPase and microtubule binding}
Discuss how other work has shown that MT affinity is controlled by registry. They do this study in vivo, and show that there is a coupling between ATPase activity and MT binding which is destroyed by locking the coiled coils into registries.

@@

\begin{itemize}
\item (apo): strong MT-binding, in $\alpha$ conformation
\item (ATP binding): causes a shift towards the $\Beta+$ conformation, causing MT dissociation by lowering affinity
\item (before ATP hydrolysis): dynein performs prestroke, \textit{then} hydrolyzes ATP
\item (during Phosphate or ADP release): MTBD rebinds to MT, returns to $\alpha$ registry, increasing the rate of product release, increasing MT affiniy, AND causing the powerstroke
\item (full release): turns back to apo dynein
\end{itemize}

>>>>

\subsection{Single-Molecule Analysis of Dynein processivity and Stepping Behavior}
Vale RD\\
2006 paper on single-molecule analysis of step sizes of dynein. Might have in-vivo velocity information.\\

@@

\subsection{Helix sliding in the stalk coiled coil of dynein couples ATPase and microtubule binding}
Takahide Kon, Kenji Imamula, Anthony J Roberts, Reiko Ohkura, Peter J Knight, I R Gibbons, Stan A Burgess & Kazuo Sutoh\\
Discuss how other work has shown that MT affinity is controlled by registry. They do this study in vivo, and show that there is a coupling between ATPase activity and MT binding which is destroyed by locking the coiled coils into registries.

@@

\begin{itemize}
\item (apo): strong MT-binding, in $\alpha$ conformation
\item (ATP binding): causes a shift towards the $\beta+$ conformation, causing MT dissociation by lowering affinity
\item (before ATP hydrolysis): dynein performs prestroke, \textit{then} hydrolyzes ATP
\item (during Phosphate or ADP release): MTBD rebinds to MT, returns to $\alpha$ registry, increasing the rate of product release, increasing MT affiniy, AND causing the powerstroke
\item (full release): turns back to apo dynein
\end{itemize}
